Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-04-10 paper/paper.tex
add subsection Qbtest

@@

\section{Results and Discussion}
Results and Discussion

>>>>

\subsubsection{Quantified Behavioral Test}
The Quantified Behavioral Test or QBTest program was written in Python and compiled using Python3.9. The package pygame was used for this interface compared to the package tkinter used for the typing test.

@@

\section{Results and Discussion}
Within-subjects testing was used.
